Part B-2

### 2024-08-27 msca-pf-part-b2-template.tex
feat: rework helper environments and showcase cv

@@

@@

@@

\begin{msctable}{
    |>{\ra}p{0.165\linewidth}
    |>{\ra}p{0.075\linewidth}
    |>{\ra}p{0.15\linewidth}
    |>{\ra}p{0.155\linewidth}
    |>{\ra}p{0.155\linewidth}
    |>{\ra}p{0.155\linewidth}
    |>{\ra}p{0.15\linewidth}|}
\hline
\rowcolor{gray!40}
\textbf{Organisation Role} &
\textbf{PIC} &
\textbf{Legal Entity Short Name} &
\textbf{Academic Organisation (Y/N)} &
\textbf{Country} &
\textbf{Name of Supervisor} \\
\hline
Beneficiary &
&
&
&
& \\
\hline
Associated partner linked to a beneficiary (if applicable) &
&
&
&
& \\
\hline
Associated partner for outgoing phase (mandatory for GF) &
&
&
&
& \\
\hline
Associated partner for secondment (optional) &
&
&
&
& \\
\hline
Associated partner for non-academic placement (optional) &
&
&
&
& \\
\hline
Other &
&
&
&
& \\
\hline
\end{msctable}

@@

\begin{msclongtable}[\small]{
    |>{\ra}p{0.3\linewidth}
    |>{\ra}p{0.66\linewidth}|}
\hline
\multicolumn{2}{|l|}{
    \textbf{[Role]}
} \\
\hline
\multicolumn{2}{|l|}{
    \textbf{[Full name + Legal Entity Short Name + Country]}
} \\
\hline
\multicolumn{2}{|l|}{
    \textbf{General description}
} \\
\hline
\textbf{Role and profile of supervisor} & \\
\hline
\textbf{Key research facilities, infrastructure and equipment} &
\emph{Demonstrate that the beneficiary has sufficient facilities and infrastructure
to host and/or offer a suitable environment for training and transfer of knowledge
to the recruited experienced researcher.}

@@

\emph{If applicable, indicate the name of the associated partner linked to a beneficiary
and describe the nature of the link in the corresponding table.} \\
\hline
\textbf{Previous and current involvement in EU-funded research and training
programmes/actions/projects} &
\emph{Indicate up to 5 relevant EU, national or international research and training
actions/projects in which the institution/department has previously participated
and/or is currently participating.} \\
\hline
\end{msclongtable}

>>>>

% {{{ commands

\NewDocumentCommand \ra {} {\raggedright\arraybackslash}

@@

% NOTE: update these as necessary
% \mscaidentifier{HORIZON-MSCA-2024-PF-01}
% \mscaproject{TDB}

@@

\subsection{Template CV}

This template is only added to showcase the commands used to create the CV. As
stated above, there is no mandatory format and these commands are mainly added
as inspiration.

\subsubsection*{Education}

\begin{cvitem}
\cventry{DD/MM/YYYY DD/MM/YYYY}{Ph.D. in Aerospace Engineering}{University Name}{Location}
\cvdetail{Title}{Title of my Ph.D}
\cvdetail{Advisor}{John Doe}
\end{cvitem}

\subsubsection*{Work Experience}

\begin{cvitem}
\cventry{DD/MM/YYYY DD/MM/YYYY}{Job Title}{Company / University}{Location}
\cvdetail{Description}{Job description in short}
\end{cvitem}

\subsubsection*{Publications}

\begin{cvitem}
\cvpub{DD/MM/YYYY}{John Doe, Jane Doe}{Title of Paper}{Journal Name, Vol. XX, pp. XX--XX}
\cvdetail{Description}{Main findings of the paper}
\cvdetail{URL}{DOI or arXiV URL}
\end{cvitem}

@@

Only relevant rows from the table should be kept.

\begin{mscaorgoverview}
Beneficiary &
&
&
&
& \\
\hline
Associated partner linked to a beneficiary (if applicable) &
&
&
&
& \\
\hline
Associated partner for outgoing phase (mandatory for GF) &
&
&
&
& \\
\hline
Associated partner for secondment (optional) &
&
&
&
& \\
\hline
Associated partner for non-academic placement (optional) &
&
&
&
& \\
\hline
Other &
&
&
&
& \\
\hline
\end{mscaorgoverview}

@@

\begin{mscaorgcapacity}
\multicolumn{2}{|l|}{
    \textbf{[Role]}
} \\
\hline
\multicolumn{2}{|l|}{
    \textbf{[Full name + Legal Entity Short Name + Country]}
} \\
\hline
\multicolumn{2}{|l|}{
    \textbf{General description}
} \\
\hline
\textbf{Role and profile of supervisor} & \\
\hline
\textbf{Key research facilities, infrastructure and equipment} &
\emph{Demonstrate that the beneficiary has sufficient facilities and infrastructure
to host and/or offer a suitable environment for training and transfer of knowledge
to the recruited experienced researcher.}

@@

\emph{If applicable, indicate the name of the associated partner linked to a beneficiary
and describe the nature of the link in the corresponding table.} \\
\hline
\textbf{Previous and current involvement in EU-funded research and training
programmes/actions/projects} &
\emph{Indicate up to 5 relevant EU, national or international research and training
actions/projects in which the institution/department has previously participated
and/or is currently participating.} \\
\hline
\end{mscaorgcapacity}
